Extending Morphological Chains with Supervised Learning and Cross-Language Features

### 2015-12-10 paper/paper.tex
more paper stuff

We used the datasets provided by 2010 Morpho Challenges. For English, this includes
a wordlist with word frequencies of approximately 878,000 words scraped from the
Wortschatz collection from the University of Leipzig, CLEF, and the Europarl corpus
as well as gold standard segmentation training and development sets of approximately 
1000 randomly selected words. Gold standard segmentation is based on the CELEX database.
For Turkish, the word list contains approximately 670,000 words, with gold standards
from a morphological parser developed at Boğaziçi University. The Turkish wordlist
was obtained from a significantly smaller corpus---at 1 million words, compared
to the English corpus of 18 million.

\subsection{Evaluation Model}

>>>>

We used the datasets provided by 2010 Morpho Challenges. For English, this includes
a wordlist with word frequencies of approximately 878,000 words scraped from the
Wortschatz collection from the University of Leipzig, CLEF, and the Europarl corpus
as well as gold standard segmentation training and development sets of approximately 
1000 randomly selected words. The MorphoChallenge 2010 gold standard segmentation is based on the CELEX database.
For Turkish, the word list contains approximately 670,000 words, with gold standards
from a morphological parser developed at Boğaziçi University. The Turkish wordlist
was obtained from a significantly smaller corpus---at 1 million words, compared
to the English corpus of 18 million. For a word-word translation dictionary,
we used a English-Turkish dictionary
(retrieved from \url{http://www.fen.bilkent.edu.tr/~aykutlu/sozluk.txt}).

\subsection{Evaluation}
Performance was measured by looking at the segmentation points within each word
(i.e. the points within the word where it is split into separate morphemes)
and evaluating the F1 measure, i.e. the harmonic mean of precision and recall;
precision is the fraction of the segmentation points that are present
in the gold segmentation; recall is the fraction of the gold segmentation points
that are correctly identified by our estimator.
